---
title: "Tutorial to reproduce the case study from Pinheiro et al. (submitted)"
output: pdf_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

knitr::knit_hooks$set(inline = function(x) {
prettyNum(x, big.mark=",")
})
```

# About

See [README](https://github.com/pinheirorbp/nestedness#readme) for
further info.

# General instructions

Use the following tutorial to reproduce the case study presented in our
paper. The file `net.txt` represents the network analyzed by
Kaiser-Bunbury et al. (2010). If you want to apply our new protocol to
your own data, just replace `net.txt` with another network of your
choice, following the same format.

The empirical network analyzed in our paper was downloaded from the [Web
of Life database](http://www.web-of-life.es) (network: M_PL_060_17). It
was originally analyzed by:

*Kaiser-Bunbury CN, Muff S, Memmott J, Muller CB, Caflisch A. 2010.
**The robustness of pollination networks to the loss of species and
interactions: a quantitative approach incorporating pollinator
behaviour**. Ecol. Lett. 13, 442-452.
<http://dx.doi.org/10.1111/j.1461-0248.2009.01437.x>.*

# Step-by-step protocol

The goal of this tutorial is to help you analyze the nestedness of an
example network using our new protocol. Most researchers measure a
network's degree of nestedness and then compare this observed value
against a randomized distribution generated with a null model, in order
to state whether the networks is "nested or not". We propose to go
beyond this dichotomic approach by assessing topology more thoroughly,
for the reasons explained in our paper.

First, we measure the nestedness observed in the network with a metric
of choice. Second, using a null model that removes all
nestedness-generating mechanisms (*equiprobable*), we create a
randomized distribution of those nestedness values. This distribution
represents what would be expected for a *non-nested topology*, to which
we compare the observed value against. Third, using a null model that
maximizes nestedness in the network (*proportional*), we create another
randomized distribution of nestedness values. This distribution
represents what would be expected for a *fully nested topology*, to
which we also compare the observed value against. This procedure leads
to four possible scenarios:

1.  If the observed value of nestedness is equal to or lower than 95%
    (or any other cut you prefer) of the randomized values that
    represent a non-nested topology, we conclude that the network's
    topology probably emerged at random, without an underlying
    mechanism;
2.  If the observed value of nestedness is higher than 95% of the
    randomized values that represent a non-nested topology, we conclude
    that the network's topology contains at least some nestedness and
    probably did not emerge at random;
3.  If the observed value of nestedness is equal to or lower than 95% of
    the randomized values that represent a fully nested topology, we
    conclude that the network's topology contains at least some
    nestedness, but that nestedness is not a good archetype to represent
    the observed structure;
4.  If the observed value of nestedness is higher than 95% of the
    randomized values that represent a fully nested topology, we
    conclude that nestedness is a good archetype to represent the
    observed structure.

Computationally, our new protocol consists of the following steps:

## Step 1

Create a new object with the network to be analyzed.

```{r}
net1 <- as.matrix(read.table("data/net.txt")) #You may use another data file of your choice
```

## Step 2

Load the required packages:

```{r message=FALSE, warning=FALSE}
library(bipartite)
```

## Step 3

Load our user-defined function to calculate nestedness and run the null
models. Check out the comments in the respective R file to obtain
detailed information about the function, including its arguments and
options.

```{r}
source("functions/nestmodels.R")
```

## Step 4

Plot the matrix to get a feeling about its structure. Visual inspection
is a key step in all kinds of numerical analysis, and we strongly
recommend it also for network analysis.

```{r matrix}
plotmatrix(net1, binary = F, 
           within_color = "#0e0a44FF", 
           base_color = "#d7d6e9ff")
```

## Step 5

The simulations included in our protocol are quite resource-consuming
and may require several minutes, depending on your computer's processing
power. Therefore, choose the number of randomized matrices (iterations)
carefully. In our paper, we ran 10,000 iterations, but we suggest
experimenting with smaller numbers first.

```{r matrices}
matrices <- 1000 #This number will be the same for all functions
```

## Step 6

Generate randomized matrices and calculate their degrees of nestedness
using different metrics.

### WNODF

Run the protocol.

```{r wnodf_plots, cache = TRUE}
WNODF=nestmodels(M=net1,
                 index="wnodf",
                 n.model = matrices,
                 prop.model = T,
                 print.at.each = 1000,
                 density.plot = T,
                 sampling.plot = T,
                 calc.at = c(50,100,200,300,400,444))
```

The **first plot** shows the distributions of randomized nestedness
values (densities) generated with the equiprobable (**red**, removes all
nestedness-generating mechanisms) and proportional (**blue**, maximizes
nestedness) null models. In **green** it shows the observed nestedness
value.

The **second plot** shows the variation in nestedness values as a
function of sampling effort (number of links in the network), for the
proportional (**blue**) and the equiprobable (**red**) null models. In
**green** it shows the observed nestedness value.

Check out the observed value and the P-values for each null model.

```{r wnod_values}
WNODF$observed
WNODF$significance
```

### WNODA

Run the protocol.

```{r wnoda_plots, cache = TRUE}
WNODA=nestmodels(M=net1,
                 index="wnoda",
                 n.model = matrices,
                 prop.model = T,
                 print.at.each = 1000,
                 density.plot = T,
                 sampling.plot = T,
                 calc.at = c(50,100,200,300,400,444))
```

The **first plot** shows the distributions of randomized nestedness
values (densities) generated with the equiprobable (**red**, removes all
nestedness-generating mechanisms) and proportional (**blue**, maximizes
nestedness) null models. In **green** it shows the observed nestedness
value.

The **second plot** shows the variation in nestedness values as a
function of sampling effort (number of links in the network), for the
proportional (**blue**) and the equiprobable (**red**) null models. In
**green** it shows the observed nestedness value.

Check out the observed value and the P-values for each null model.

```{r wnoda_values}
WNODA$observed
WNODA$significance
```

### NODF

#### Accounting for weighted marginal sums

Run the protocol.

```{r nodf1_plots, cache = TRUE}
NODF1=nestmodels(M=net1,
                 index="nodf",
                 n.model = matrices, 
                 prop.model = T,
                 equi.model = T,
                 print.at.each = 1000,
                 density.plot = T,
                 wprob = T,
                 wsamp=F)
```

The **plot** shows the distributions of randomized nestedness values
(densities) generated with the equiprobable (**red**, removes all
nestedness-generating mechanisms) and proportional (**yellow**,
maximizes nestedness, considering link weights) null models. In
**green** it shows the observed nestedness value.

Check out the observed value and the P-values for each null model.

```{r nodf1_values}
NODF1$observed
NODF1$significance
```

#### Using only binary information

Run the protocol.

```{r nodf2_plots, cache = TRUE}
NODF2=nestmodels(M=net1,
                 index="nodf",
                 n.model = matrices, 
                 prop.model = T,
                 equi.model = T,
                 print.at.each = 1000,
                 density.plot = T,
                 wprob = F,
                 wsamp=F)
```

The **plot** shows the distributions of randomized nestedness values
(densities) generated with the equiprobable (**red**, removes all
nestedness-generating mechanisms) and proportional (**yellow**,
maximizes nestedness, but ignoring link weights) null models. In
**green** it shows the observed nestedness value.

Check out the observed value and the P-values for each null model.

```{r nodf2_values}
NODF2$observed
NODF2$significance
```
